---
title: 
author: 
date: 
output: html_document
---

# Note that this R markdown code includes 'code chunks' that specify settings
# You may use multiple R code chunks if you want settings to differ between them, or if
# you generally want to run only certain code chunks at a time step by step
# Code chunks are indicated by the triple backticks with the r within curly braces, which
# may have additional options

# Load packages:

```{r setup, include=FALSE}
# These packages all need to be installed for the work today
# This first knitr command sets various settings, importantly it
# sets the working directory to the folder this file is contained in

# Eventually we may use knitr, but here is enough
# knitr::opts_chunk$set(echo = TRUE)
library(here) # Use here to refer to the relative path of the object within the project folder!
# Specify the project's path
# MAKE SURE TO CHANGE THE FILENAME OF TEMPLATE IF YOU CHANGE FILENAME OF THIS SCRIPT
i_am("template.Rmd") 
# Put other libraries here

```

## Remaining code
```{r}
# Put code here

```